Memory for television episodes preserves event content while introducing new across-event similarities

### 2020-02-03 paper/main.tex
recompiled with updated figs

\begin{figure}[tp]
  \centering
  \includegraphics[width=1\textwidth]{figs/precision_detail}
  \caption{\small \textbf{Precision metric reflects quality and specificity of recall.} \textbf{A.} Recall precision distributions over participants, for each video event.  Grey violin plots display kernel density estimates for the distribution of recall precision scores for a single video event.  Colored dots within the violin plots represent each participant's recall precision for that event.  Video events are ordered along the $x$-axis by the average precision with which they were remembered.  \textbf{B.} The set of text annotatations (generated by \citealp{ChenEtal17}) comprising 
   \textbf{C.} }
  \label{fig:precision-detail}
\end{figure}

>>>>

\begin{figure}[tp]
  \centering
  \includegraphics[width=1\textwidth]{figs/precision_detail}
  \caption{\small \textbf{Precision metric reflects completeness of recall.} \textbf{A.} Recall precision distributions over participants, for each video event.  Grey violin plots display kernel density estimates for the distribution of recall precision scores for a single video event.  Colored dots within the violin plots represent individual participants' recall precision for that event.  Video events are ordered along the $x$-axis by the average precision with which they were remembered.  \textbf{B.} The set of ``Narrative details" video annotations (generated by \citealp{ChenEtal17}) for scenes comprising an example video event (22) identified by the HMM.  Each action or feature is highlighted in a different color.  \textbf{C.} A subset of the sentences comprising the most precise (P17) and least precise (P6) participants' recalls of video event 22.  Descriptions of specific actions or features reflecting those highlighted in panel B are highlighted in the corresponding color.}
  \label{fig:precision-detail}
\end{figure}

\begin{figure}[tp]
  \centering
  \includegraphics[width=1\textwidth]{figs/distinctiveness_detail}
  \caption{\small \textbf{Distinctiveness metric reflects specificity of recall.} \textbf{A.} Recall precision distributions over participants, for each video event.  Grey violin plots display kernel density estimates for the distribution of recall precision scores for a single video event.  Colored dots within the violin plots represent individual participants' recall precision for that event.  Video events are ordered along the $x$-axis by the average precision with which they were remembered.  \textbf{B.} The set of ``Narrative details" video annotations (generated by \citealp{ChenEtal17}) for scenes comprising an example video event (22) identified by the HMM.  Each action or feature is highlighted in a different color.  \textbf{C.} A subset of the sentences comprising the most precise (P17) and least precise (P6) participants' recalls of video event 22.  Descriptions of specific actions or features reflecting those highlighted in panel B are highlighted in the corresponding color.}
  \label{fig:distinctiveness-detail}
\end{figure}
